### 2019-08-22 reports/thesis/chapters/3_compoundPoisson.tex
Compound Poisson
Typo in CompoundPoisson.m for the objective function
Few formatting changes and typo in report
Adjust compound Poisson chapter
Revise compoundpoisson

Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log likelihood is defined to be
\begin{align}
  \ln L(\lambda,\alpha,\beta;X) &= \sum_{i=1}^n
  \left[
    \mathbb{I}(x_i=0)\ln \prob(X=x_i)
    +\mathbb{I}(x_i>0)\ln p_X(x_i)
  \right]
  \nonumber \\
  &\!\begin{multlined}[b]
  =
    \sum_{i=1}^n
    \left[
      -\mathbb{I}(x_i=0)\lambda
      \vphantom{\sum_i^i}
    \right.
    {}\\
    \left.
      +\mathbb{I}(x_i>0)\left(
      -1-\beta x_i-\lambda-\ln x -\ln\sum_{y=1}^\infty W_y
      \right)
    \right] \ .
  \end{multlined}
\end{align}
$\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.

>>>>

Let $\widehat{\lambda}$, $\widehat{\alpha}$ and $\widehat{\beta}$ be estimators of $\lambda$, $\alpha$ and $\beta$ respectively. The log likelihood is defined to be
\begin{equation*}
  \ln L(\lambda,\alpha,\beta;X) = \sum_{i=1}^n
  \left[
    \mathbb{I}(x_i=0)\ln \prob(X=x_i)
    +\mathbb{I}(x_i>0)\ln p_X(x_i)
  \right]
\end{equation*}
and using the results in Appendix \ref{chapter:appendix_tweedie}
\begin{equation}
  \ln L(\lambda,\alpha,\beta;X) =
    \sum_{i=1}^n
    \left[
      -\mathbb{I}(x_i=0)\lambda
      \vphantom{\sum_i^i}
    \right.
    {}\\
    \left.
      +\mathbb{I}(x_i>0)\left(
      -\beta x_i-\lambda-\ln x +\ln\sum_{y=1}^\infty W_y
      \right)
    \right] \ .
\end{equation}
Maximum likelihood estimators are values of $\lambda$, $\alpha$ and $\beta$ which jointly maximises the log likelihood.
